The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-21 Paper/v4/Article_UV_Mexico.tex
Rename paper folders

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM).
Measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated for the period 2000-2019,
except for the year 2011 which contained large data gaps and was therefore not used.
A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
significantly change the trends calculated for this.\citep{Carabali_2017}
Only 8\% of the data between the years 2014 and 2019 were missing.
The largest data gap occurred in 2018 when the instrument was returned for calibration.

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated collaboratively by the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface. Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.\cite{Tanskanen_2007} A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for typical cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
The selection of cloud-free days was aided by comparison of the measurements
with the TUV model predictions for clear skies, with prolonged deviations and
fluctuations usually indicative of cloudy conditions. However,
during the rainy period (from June to October) at least a brief episode of clouds,
is seen at CHO station around noon on 23 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

@@

Comparisons of OMI with ground-based UV measurements have been reviewed
recently by \citet{Zhang_2019} and \citet{Vitt_2020}.
OMI-derived UV generally overestimates
ground-level measurements by 1-10\% in relatively clean conditions (e.g.
rural U.S), by 10-30\% in Southern Europe and by 40\% or more in
Santiago, Chile\citep{Cabrera_2012} and Thailand\citep{Janjai_2013}. The
overestimations appear related in large part to incomplete accounting of
UV absorption by BL aerosol, although other factors such as the
correction to solar noon may also introduce some
bias.\citep{Zhang_2019} Over Europe, ground-based UVI observations for
several decades are systematically lower than those estimated from
satellites even after consideration of climatological aerosol
distributions, showing the importance of local pollution not resolved
from space.\citep{Vitt_2020} However, the difference between
satellite-derived and ground-based UVI was less than 1.0 UVI units in
over 90\% of the cases, in contrast to the difference of 3-5 units found
here for Mexico City (Table~{\ref{461017}}).

@@

UV reductions by air pollutants are expected to be most severe near the
surface, while chemical reactions leading to photochemical smog occur
throughout the vertical extent of the BL.
Figure~{\ref{973680}} shows the vertical profiles of
photolysis coefficients (the reciprocals of photolytic lifetimes) computed with the TUV model, for
two key reactions, the photolysis of O\textsubscript{3} to yield excited
oxygen atoms O(1D), and the photolysis of NO\textsubscript{2}. In the
absence of optically active pollutants, these coefficients would be
nearly independent of altitude in the BL. However, the presence of
pollutants leads to a strong decrease toward the surface, with notably
more severe reductions in 2000 compared to 2019.~While the specific
values shown in the figure are only illustrative for typical conditions,
routine daily air quality modeling should carefully account for the long
term variations in these photolysis coefficients.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/jvals}
    \caption{{Vertical profiles of the photolysis coefficients for the
          reaction~\(O_3 + h\nu \rightarrow O(1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
          axis, red) for zero pollution (solid) and Mexico City in the years 2000
          (dashed) and 2019 (dotted). TUV calculation for 21 June at solar noon.
            {\label{973680}}%
        }}
  \end{center}
\end{figure}

@@

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below values derived from satellite-based
observations. Although ideally both data sets should match,
the satellite has a limitation to seeing boundary layer absorbers.
Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
When typical values of pollutant: aerosols,
tropospheric ozone, NO\textsubscript{2}
and SO\textsubscript{2}, are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality over the last two decades,
were accompanied by statistically significant increases in the
observed UVI, in agreement with the model-predicted changes.

>>>>

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM).
Measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated for the period 2000-2019,
except for the year 2011 which contained large data gaps and was therefore not used.
A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
significantly change the trends calculated for this time period.\citep{Carabali_2017}
Only 8\% of the data between the years 2014 and 2019 were missing.
The largest data gap occurred in 2018 when the instrument was returned for calibration.

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated collaboratively by the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (13:00h - 15:00h CST).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface. Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.\cite{Tanskanen_2007} A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for typical cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
The selection of cloud-free days was aided by comparison of the measurements
with the TUV model predictions for clear skies, with prolonged deviations and
fluctuations usually indicative of cloudy conditions. However,
during the rainy period (from June to October) at least a brief episode of clouds
is seen at CHO station around noon on 23 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

@@

Comparisons of OMI with ground-based UV measurements have been reviewed
recently by \citet{Zhang_2019} and \citet{Vitt_2020}.
OMI-derived UV generally overestimates
ground-level measurements by 1-10\% in relatively clean conditions (e.g.
rural U.S), by 10-30\% in Southern Europe and by 40\% or more in
Santiago, Chile\citep{Cabrera_2012} and Thailand\citep{Janjai_2013}. The
overestimations appear related in large part to incomplete accounting of
UV absorption by BL aerosol, although other factors such as the
correction to solar noon may also introduce some
bias.\citep{Zhang_2019} Over Europe, ground-based UVI observations for
several decades are systematically lower than those estimated from
satellites even after consideration of climatological aerosol
distributions, showing the importance of local pollution not resolved
from space.\citep{Vitt_2020} However, the difference between
satellite-derived and ground-based UVI was less than 1.0 UVI units in
over 90\% of the cases, in contrast to the difference of 3-5 units found
here for Mexico City.

@@

UV reductions by air pollutants are expected to be most severe near the
surface, while chemical reactions leading to photochemical smog occur
throughout the vertical extent of the BL.
Figure~{\ref{973680}} shows the vertical profiles of
photolysis coefficients (the reciprocals of photolytic lifetimes) computed with the TUV model, for
two key reactions, the photolysis of O\textsubscript{3} to yield excited
oxygen atoms O(\textsuperscript{1}D), and the photolysis of NO\textsubscript{2}. In the
absence of optically active pollutants, these coefficients would be
nearly independent of altitude in the BL. However, the presence of
pollutants leads to a strong decrease toward the surface, with notably
more severe reductions in 2000 compared to 2019.~While the specific
values shown in the figure are only illustrative for typical conditions,
routine daily air quality modeling should carefully account for the long
term variations in these photolysis coefficients.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/jvals}
    \caption{{Vertical profiles of the photolysis coefficients for the
          reaction~\(O_3 + h\nu \rightarrow O(^1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
          axis, red) for zero pollution (solid) and Mexico City in the years 2000
          (dashed) and 2019 (dotted). TUV calculation for 21 June at solar noon.
            {\label{973680}}%
        }}
  \end{center}
\end{figure}

@@

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below values derived from satellite-based
observations. Although ideally both data sets should match,
the limited ability of satellites to detect BL absorbers means that they cannot reveal long-term UV trends.
Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
When typical values of pollutant aerosols,
tropospheric ozone, NO\textsubscript{2}
and SO\textsubscript{2}, are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality over the last two decades
were accompanied by statistically significant increases in the
observed UVI, in agreement with the model-predicted changes.
